Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-08 edubots_surveys.Rnw
Fix by @noorhanabbas closes #58

WhatsApp is, at least in most Western countries, the most popular MIM platform
used by educators to give assignments' feedback to students, support course
discussions, and provide learning resources in informal learning settings
\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
enhance social presence \cite{tang2017mobile} and foster trust relationships
between educators and students embedded in the social learning process
\cite{gachago2015crossing}; however, this last paper also reflects the need for
learners to ``take ownership of the tool'' and the advantages of social learning
in general. At the same time, it also mentions different challenges, among which
the most important is the blurring of social and academic life. Examining these
opinions will be the objective of RQ3 in this paper.

>>>>

WhatsApp is, at least in most Western countries, the most popular MIM platform
used by educators to \textcolor{blue}{provide} assignments' feedback to students, support course
discussions, and provide learning resources in informal learning settings
\cite{panah2020study}.  Moreover, the use of WhatsApp in higher education could
enhance social presence \cite{tang2017mobile} and foster trust relationships
between educators and students embedded in the social learning process
\cite{gachago2015crossing}; however, this last paper also reflects the need for
learners to ``take ownership of the tool'' and the advantages of social learning
in general. At the same time, it also mentions different challenges, among which
the most important is the blurring of social and academic life. Examining these
opinions will be the objective of RQ3 in this paper.
